Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-08 doc/paper-lcr.tex
draft update

For real lines of sight, 
\phil{we would like to estimate the external convergence as best we can given all
data available. Typically this data is in the form of a photometric galaxy
catalog, containing positions, brightnesses, colours, and other type
information for each galaxy in the field of the lens, down to some magnitude
limit. Since we do not observe halo mass directy, we need some way of estimating
the mass of each galaxy in the catalog, so that we can compute its
contribution to $\kappax$. This mass assignment recipe will be uncertain, but
can be calibrated to cosmological simulations.}

@@

Cosmological dark matter simulations can be used to generate mock lines of
sight...
\todo{Stefan}{Write section on how the ray tracing was done and how halos are extracted from
 the MS n-body particles}

\phil{Transforming the photometometric galaxy catalogue into a}  catalogue of
halo masses, positions, and redshifts, will enable us to attempt a
reconstruction of the convergence induced by every halo near a line of sight.
This is the subject of the first subsection below. We also need to account for
the mass in the Universe that is not associated with the galaxies we can see
-- this is the subject of the second subsection below.

>>>>

For real lines of sight, we would like to estimate the external convergence as best we can given all
data available. Typically this data is in the form of a photometric galaxy
catalog, containing positions, brightnesses, colours, and possibly spectra for each galaxy in the
field of the lens, down to some magnitude
limit. Since we can not observe the surface mass density of each halo
directy, we need some way of estimating
the mass of each halo in the catalog, so that we can compute its
contribution to the total $\kappax$ along the line of sight. This mass assignment recipe will be uncertain, but
can be calibrated with cosmological simulations.

@@

Cosmological dark matter simulations can be used to generate mock lines of
sight and can be raytraced through to give each mock sightline a $\kappax$ value...
\todo{Stefan}{Write section on how the ray tracing was done and how halos are extracted from
 the MS n-body particles}

Transforming the photometometric galaxy catalogue into a  catalogue of
halo masses, positions, and redshifts, will enable us to attempt a
reconstruction of the convergence induced by every halo near a line of sight.
This is the subject of the first subsection below. We also need to account for
the mass in the Universe that is not associated with the galaxies we can see
-- this is the subject of the second subsection below.
